Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
adding submission number
intro S4.4

Program slicing is a program understanding technique to identify the
relevant parts of the program with respect to given points of
interest.  Dynamic
slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
  static
  slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
has been shown useful in automated software debugging where the region
of interest is restricted to what can be reached from failing
tests. Several dynamic slicing techniques exist. This paper uses
Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality.\comments{ In constrast with alternative slicing
  implementations based on dependency
  chains~\cite{Tip:1994:SPS:869354}\comments{(\eg{},
    JSlice~\cite{Wang:2004:UCB:998675.999455} and
    JavaSlicer~\cite{hammacher-bachthesis-2008})},} Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices.  Critical Slicing simplifies the original
program such that the resulting program preserves critical
observations, such as assertion violations. More precisely, the
simplification mechanism consists of deleting statements on the
original program and checking if the output of the original and
modified program are the same.

@@

This subsection aims to report the performance of the \ds{} technique on slicing de faults of $5$ \dfj{} projects. Table \ref{tab:red}
presents the reduction percentage obtained for each project after slicing the top $5$ and $10$ of classes comprising the highest faulty statements. Our approach was capable to reduce the \dfj{} projects in an average of 30.23\%.

@@

The following section aims to answer the research questions presented previously.

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 584.33 (580.03)  &  516.42 (502.60) & 679.67 (566.99) & 613.98 (491.47)  \\ \midrule
Median & 49.38 (47.5)   & 53.00 (54.5)  & 69.25 (42.72)             & 56.93 (40)\\ \midrule
Variance & 1223.08 (1236.94)  &  1148.11 (1149.09)  & 1352.37 (1229.4) & 1294.87  (1143.02) \\ \midrule
Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 69.51 \\ p-value = 5.44 x $10^{-15}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}

>>>>

Program slicing is a program understanding technique to identify the
relevant parts of the program with respect to given points of
interest. Dynamic
slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
static slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
has been shown useful in automated software debugging where the region
of interest is restricted to what can be reached from failing
tests. Several dynamic slicing techniques exist. This paper uses
Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality. Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices.  Critical Slicing simplifies the original
program such that the resulting program preserves critical
observations, such as assertion violations. More precisely, the
simplification mechanism consists of deleting statements on the
original program and checking if the output of the original and
modified program are the same.

@@

This subsection aims to report the performance of the \ds{} technique on slicing de 
faults of $5$ \dfj{} projects. Table \ref{tab:red}
presents the reduction percentage obtained for each project after slicing the top 
$5$ and $10$ of classes comprising the highest faulty statements. Our approach was 
capable to reduce the \dfj{} projects in an average of $30.23\%$.

@@

Our approach was capable of slicing a total of $260$ faults from $5$ different 
sujects. We are still running experiments for the \closure{} and \cmath{} projects.
(The results of these faults will be integrated on the camera-ready if accepted).
$33$ of the $260$ faults do not include the faulty statements in the slicer report
after slicing.

@@

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 584.33 (580.03)  &  516.42 (502.60) & 679.67 (566.99) & 613.98 (491.47)  \\ \midrule
Median & 49.38 (47.5)   & 53.00 (54.5)  & 69.25 (42.72)             & 56.93 (40)\\ \midrule
Variance & 1223.08 (1236.94)  &  1148.11 (1149.09)  & 1352.37 (1229.4) & 1294.87  (1143.02) \\ \midrule
Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 69.51 \\ p-value = 5.44 x $10^{-15}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table*}
